### 2024-11-14 README.Rmd
update README

<!-- badges: start -->
<!-- badges: end -->

@@

hatchR is a tool that allow users to leverage daily temperature records to predict when a fish is expected to hatch and/or emerge using statistical models.

Specifically, hatchR is intended to bridge the analytic gap of taking statistical models developed in hatchery settings (e.g., Beacham and Murray 1990) and applying them to real world temperature data sets using the effective value framework developed by Sparks et al. (2019).

@@

``` r
# install.packages("pak")
pak::pak("bmait101/hatchR")
```
## Usage

@@

@@

>>>>

<!-- badges: start -->

<!-- badges: end -->

@@

`hatchR` is an R package for predicting fish developmental phenology using statistical models. It is intended to bridge the analytic gap of taking statistical models developed in hatchery settings (e.g., Beacham and Murray 1990) and applying them to real world temperature data sets using the effective value framework developed by Sparks et al. (2019).

@@

``` r
# install.packages("pak")
pak::pak("bmait101/hatchR")
```

## Usage

@@

## Suggested Packages

`hatchR` suggests the following **R** Packages:

* `ggplot2` - for vignette vizualizations.
* `lubridate` - for date-time manipulation.
* `knitr`: For vignette building.
* `rmarkdown`: For vignette building.
* `testthat`: For unit testing.

@@

## License

This project is licensed under the GNU General Public License, [GPL-3](https://cran.r-project.org/web/licenses/GPL-3).

## Disclaimer

`hatchR` project code is provided on an "as is" basis and the user assumes responsibility for its use. USDA Forest Service has relinquished control of the information and no longer has responsibility to protect the integrity , confidentiality, or availability of the information. Any reference to specific commercial products, processes, or services by service mark, trademark, manufacturer, or otherwise, does not constitute or imply their endorsement, recommendation or favoring by USDA Forest Service.
